An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-23 scagnostics.Rmd
Citation added.

[@Grimm2016] explored the behaviour of scagnostics for selecting variables, and proposed two more, based on smoothing splines and distance correlation, that have some nicer properties. In addition the availability of another two indices based on information criteria, maximal and total information coefficient (MIC and TIC) [@Reshef1518] round out our collection of metrics. \footnote{It is interesting to note that entropy, closely related to the notion of mutual information, has previously been considered as a projection pursuit index when searching for interesting one-dimensional projections, see \cite{nason1992}, \cite{NIPS1997_1408}.}
These indices are all available in R packages [@rref]: scagnostics [@HWscagR], mbgraphic [@mbgraphic] and minerva [@minerva]. The projection pursuit guided tour is available in the R package, tourr [@tourr].

>>>>

[@Grimm2016] explored the behaviour of scagnostics for selecting variables, and proposed two more, based on smoothing splines and distance correlation, that have some nicer properties. In addition the availability of another two indices based on information criteria, maximal and total information coefficient (MIC and TIC) [@Reshef1518] round out our collection of metrics. \footnote{It is interesting to note that entropy, closely related to the notion of mutual information, has previously been considered as a projection pursuit index when searching for interesting one-dimensional projections, see discussion in \cite{huber1985,jones87}.}
These indices are all available in R packages [@rref]: scagnostics [@HWscagR], mbgraphic [@mbgraphic] and minerva [@minerva]. The projection pursuit guided tour is available in the R package, tourr [@tourr].
